\begin{thebibliography}{69}

% AUTHOR - TITLE - YEAR

\bibitem{kay_arulkumaran} Kai Arulkumaran, Marc Peter Deisenroth, Miles Brundage, Anil Anthony Bharath. "A Brief Survey of Deep Reinforcement Learning (BMVC)" (2017).

\bibitem{volodymyr_mnih} Volodymyr Mnih, Adria Puigdomenech Badia, Mehdi Mirza, Alex Graves, Timothy P Lillicrap, Tim Harley, David Silver, and Koray Kavukcuoglu. "Asynchronous Methods for Deep Reinforcement Learning" (2016).

\bibitem{sutton_barto} Richard S. Sutton and Andrew G. Barto. "Reinforcement Learning: An Introduction" (2014, 2015, 2016, 2017).

\bibitem{christopher_watkins} Christopher JCH Watkins and Peter Dayan. "Machine Learning"  (1992).

\bibitem{volodymyr_mnih_koray_kavukcuoglu} Volodymyr Mnih, Koray Kavukcuoglu, David Silver, Alex Graves, Ioannis Antonoglou, Daan Wierstra, Martin Riedmiller. "Playing Atari with Deep Reinforcement Learning" (2018).

\bibitem{volodymyr_mnih_david_silver} Volodymyr Mnih, Koray Kavukcuoglu, David Silver, Andrei A Rusu, Joel Veness, Marc G Bellemare, Alex Graves, Martin Riedmiller, Andreas K Fidjeland, Georg Ostrovski, et al. "Human-Level Control through Deep" (2015).

\bibitem{miles_brundage} Miles Brundage Anil Anthony Bharath. Kai Arulkumaran, Marc Peter Deisenroth. "A brief survey of Deep Reinforcement Learning" (2017).

\bibitem{miles_brundage} Gavin A Rummery and Mahesan Niranjan. "On-line q-learning using \textit{connectionistsystems}" (1994).

\bibitem{jan_peters} Jan Peters Daan Wierstra, Alexander Forster and Jurgen Schmidhuber. "Recurrentpolicy gradients" (2010).

\bibitem{gradient} Sebastian Ruder. "An overview of gradient descent optimization algorithms" (2017).

\bibitem{faustino_gomez} Faustino Gomez and Jurgen Schmidhuber. "Evolving modular fast-weight networks forcontrol" (2005).

\bibitem{satinder_singh} Satinder Singh Yishay Mansour Richard S. Sutton, David McAllester. Policy gradient methods for reinforcement learning with function approximation" (1999).

\bibitem{pieter_abbeel} Pieter Abbeel Justin Fu, Sergey Levine.  "One-shot learning of manipulation skills withonline dynamics adaptation and neural network priors" (2016).

\bibitem{naveen_venkat} Naveen Venkat. The curse of dimensionality. Inside out" (2018).

\bibitem{eric_kolve} Eric Kolve Joseph J. Lim Abhinav Gupta Li Fei-Fei Ali Farhadi Yuke Zhu,Roozbeh Mottaghi. "Target-driven visual navigation in indoor scenes using deep re-inforcement learning" (2016).

\bibitem{mehdi_mirza} Mehdi Mirza Alex Graves Timothy P Lillicrap Tim Harley David SilverVolodymyr Mnih, Adria Puigdomenech Badia and Koray Kavukcuoglu. "Asynchronous methods for deep reinforcement learning" (2016).

\bibitem{multi_armed} Varaiya, P. and Walrand, J. C. "Multi-armed bandit problems and resource sharing systems. In Computer Performance and Reliability, Proceedings of the International Workshop" (1983).

\bibitem{temporal_difference_learning} J. N. Tsitsiklis and B. V. Roy, “Average cost temporal-difference learning" (1999).

\bibitem{markov_decision_process} Bellman, R. “A Markovian decision process.” Technical report, DTIC Document (1957).

\bibitem{dynamic_programming} Bertsekas, D. and Tsitsiklis, J. Neuro-Dynamic Programming. Belmond, MA: Athena Scientific (1996).

\bibitem{montecarlo} J.-C. Walter and G. T. Barkema. "An introduction to Monte Carlo methods" (1999).

\bibitem{thomas_b_sch} Thomas B Sch on Niklas Wahlstrom and Marc P Deisenroth. Learning deep dynamicalmodels from image pixels (2015).

\bibitem{david_silver} David Silver Andrei A Rusu Joel Veness Marc G Bellemare Alex Graves Mar-tin Riedmiller Andreas K Fidjeland Georg Ostrovski et al. Volodymyr Mnih, Ko-ray Kavukcuoglu. "Human-level control through deep" (2015).

\bibitem{mohamed_medhat} Mohamed Medhat Gaber, Ahmed Hussein and Eyad Elyan. "Deep active learning forautonomous navigation" (2016).

\bibitem{ronan_collobert} Ronan Collobert Yoshua Bengio, Jerome Louradour and Jason Weston. "Curriculum learning" (2009).

\bibitem{nando_de_freitas} Nando de Freitas Jakob Foerster, Yannis M Assael and Shimon Whiteson. "Learning tocommunicate with deep multi-agent reinforcement learning" (2016).

\bibitem{eric_tzeng} Eric Tzeng, Coline Devin, Judy Hoffman, Chelsea Finn, Xingchao Peng, Sergey Levine, Kate Saenko, and Trevor Darrell. "Towards Adapting Deep Visuomotor Representations from Simulated to Real Environments" (2016).

\bibitem{tejas_d_kulkarni} Tejas D Kulkarni Tom Erez Peter Battaglia Misha Denil, Pulkit Agrawal and Nandode Freitas. "Learning to 
perform physics experiments via deep reinforcement learning" (2017).

\bibitem{hrl} Dagui Chen1, Qi Yan1, Shangqi Guo1, Zhile Yang1, Xin Su1 and Feng Chen. "Learning Effective Subgoals with Multi-Task Hierarchical. Reinforcement Learning" (2019).

\bibitem{oliver_cameron} Oliver Cameron. "Advancing Self-Driving Cars with Reinforcement and Imitation Learning" (2020).

\bibitem{rl_basado_en_modelo} Łukasz Kaiser, Mohammad Babaeizadeh, Piotr Miłos, Błażej Osiński, Roy H Campbell, Konrad Czechowski, Dumitru Erhan, Chelsea Finn, Piotr Kozakowski, Sergey Levine, Afroz Mohiuddin, Ryan Sepassi, George Tucker, Henryk Michalewski. "Model Based Reinforcement Learning for Atari" (2020).

\bibitem{world_models} David Ha, Jürgen Schmidhuber. "World Models" (2018).

\bibitem{robotica_industrial} `Crecimiento de la robótica en la última década'. \href{https://www.interempresas.net/Robotica/Articulos/254914-Crece-un-6-por-ciento-el-numero-de-robots-industriales-instalados-en-todo-el-mundo-en-2018.html}

\bibitem{gym_gazebo} \href{https://github.com/erlerobot/gym-gazebo}{Librería Gym Gazebo (erlerobot)}: \url{https://github.com/erlerobot/gym-gazebo}.

\bibitem{paper_gym_gazebo} Extending the OpenAI Gym for robotics: a toolkit for reinforcement learning using ROS and Gazebo \href{https://arxiv.org/pdf/1608.05742.pdf}(Paper del software Gym Gazebo (2016).)

\bibitem{gym} \href{https://gym.openai.com/}{Gym, de OpenAI. Librería para entrenamiento de entornos utilizando el aprendizaje por refuerzo.}

\bibitem{oreily} Aurélien Géron. "Hands-On Machine Learning with Scikit-Learn, Keras, and TensorFlow, 2nd Edition" (2019) \url{https://www.oreilly.com/library/view/hands-on-machine-learning/9781492032632/}.

\bibitem{pytorch_drl} Maxim Lapan. "Deep Reinforcement Learning Hands-On - Second Edition." (2020) \ur{https://www.packtpub.com/product/deep-reinforcement-learning-hands-on-second-edition/9781838826994}

\end{thebibliography}
